### 2015-04-20 paper.tex
Add figure
Add power and drag coefficient curves
Add figure captions
Comment out figures on master branch
Add wake characteristic figures

@@

\subsection*{Sed ac quam id nisi malesuada congue.}

@@

>>>>

\subsection*{Performance}

@@

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/cp_curves}
\caption{{\bf Power Coefficient Curves.}
Mean rotor power coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}
\label{cp-curves}
\end{figure}

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/cd_curves}
\caption{{\bf Drag Coefficient Curves.}
Mean rotor drag coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}
\label{cd-curves}
\end{figure}

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/re_dep_cp}
\caption{{\bf Figure Title first bold sentence Nulla mi mi, venenatis sed ipsum 
varius, volutpat euismod diam.}
Figure Caption Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim 
rutrum. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
\label{cp-re-dep}
\end{figure}

\subsection*{Wake characteristics}

@@

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/meancontquiv}
\caption{{\bf Near-Wake Mean Velocity Field.}
Mean velocity field at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
$\lambda=3.1$.}
\label{meancontquiv}
\end{figure}

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/k_contours}
\caption{{\bf Turbulence Kinetic Energy.}
Turbulence kinetic energy at 1 m downstream ($x/D=0.93$), $U_\infty=1.0$ m/s, and
$\lambda=3.1$.}
\label{kcont}
\end{figure}
